### 2022-12-07 output/01_exploratory/tables/bldg_val_results_table.tex
Created estimation tables

{
\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}
\begin{tabular}{l*{4}{c}}
\toprule
                    &\multicolumn{1}{c}{\hspace{0.25cm}Building value}&\multicolumn{1}{c}{\hspace{0.25cm}Building value}&\multicolumn{1}{c}{\hspace{0.25cm}Building value}&\multicolumn{1}{c}{\hspace{0.25cm}Building value}\\
                    &        b/se&        b/se&        b/se&        b/se\\
\midrule
judgment\_for\_plaintiff& 2434984.290& 1161293.951& 1161293.951& 1055231.099\\
                    & (588147.83)& (453836.79)& (453836.79)&(2319051.94)\\
\midrule
Observations        &        5567&        5567&        5567&        5567\\
\bottomrule
\end{tabular}
}

>>>>

{
\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}
\begin{tabular}{l*{4}{c}}
\toprule
                    &\multicolumn{1}{c}{\hspace{0.25cm}Building value}&\multicolumn{1}{c}{\hspace{0.25cm}Building value}&\multicolumn{1}{c}{\hspace{0.25cm}Building value}&\multicolumn{1}{c}{\hspace{0.25cm}Building value}\\
                    &        b/se         &        b/se         &        b/se         &        b/se         \\
\midrule
judgment\_for\_plaintiff& 2434984.290\sym{***}& 1161293.951\sym{*}  & 1161293.951\sym{*}  & 1055231.099         \\
                    & (588147.83)         & (453836.79)         & (453836.79)         &(2319051.94)         \\
\midrule
Observations        &        5567         &        5567         &        5567         &        5567         \\
$\text{R}^2$        &     0.00307         &       0.491         &       0.491         &       0.527         \\
City F.E.           &          No         &         Yes         &         Yes         &          No         \\
Year F.E.           &          No         &         Yes         &         Yes         &          No         \\
Case Controls       &          No         &          No         &         Yes         &          No         \\
I.V. Estimate       &          No         &          No         &          No         &         Yes         \\
\bottomrule
\end{tabular}
}

### 2022-12-07 output/01_exploratory/tables/total_val_results_table.tex
Created estimation tables

{
\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}
\begin{tabular}{l*{4}{c}}
\toprule
                    &\multicolumn{1}{c}{\hspace{0.25cm}Total property value}&\multicolumn{1}{c}{\hspace{0.25cm}Total property value}&\multicolumn{1}{c}{\hspace{0.25cm}Total property value}&\multicolumn{1}{c}{\hspace{0.25cm}Total property value}\\
                    &        b/se&        b/se&        b/se&        b/se\\
\midrule
judgment\_for\_plaintiff& 3259177.986& 1507062.672& 1507062.672&  751962.414\\
                    & (762388.53)& (577088.19)& (577088.19)&(2866558.93)\\
\midrule
Observations        &        5567&        5567&        5567&        5567\\
\bottomrule
\end{tabular}
}

>>>>

{
\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}
\begin{tabular}{l*{4}{c}}
\toprule
                    &\multicolumn{1}{c}{\hspace{0.25cm}Total property value}&\multicolumn{1}{c}{\hspace{0.25cm}Total property value}&\multicolumn{1}{c}{\hspace{0.25cm}Total property value}&\multicolumn{1}{c}{\hspace{0.25cm}Total property value}\\
                    &        b/se         &        b/se         &        b/se         &        b/se         \\
\midrule
judgment\_for\_plaintiff& 3259177.986\sym{***}& 1507062.672\sym{**} & 1507062.672\sym{**} &  751962.414         \\
                    & (762388.53)         & (577088.19)         & (577088.19)         &(2866558.93)         \\
\midrule
Observations        &        5567         &        5567         &        5567         &        5567         \\
$\text{R}^2$        &     0.00327         &       0.510         &       0.510         &       0.549         \\
City F.E.           &          No         &         Yes         &         Yes         &          No         \\
Year F.E.           &          No         &         Yes         &         Yes         &          No         \\
Case Controls       &          No         &          No         &         Yes         &          No         \\
I.V. Estimate       &          No         &          No         &          No         &         Yes         \\
\bottomrule
\end{tabular}
}
